\documentclass[margin]{res}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

\usepackage{latexsym}   % to get the \Box symbol


%\oddsidemargin -.4in
%\evensidemargin -.4in
%\textwidth=5.9in
%\topmargin=-0.4in
%\setlength{\textheight}{9.9in}

\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}
\name{\LARGE \bf POOYA JAFERIAN \vspace*{.1in}}
\address{2106 668 Citadel Parade \\ Vancouver, BC V6B 1W6 \\ (778) 322-0513}
%\address{\ {\it E-mail:}  pooya@ece.ubc.ca \\}
%\address{2106 668 Citadel Parade\\ Vancouver, BC Canada V6B 1W6}
\address{http://pooya.jaferian.com\\ pooya@ece.ubc.ca \\}

\begin{resume}

\section{\sc Skills and Strengths}
\begin{description}
  \item[UX Research and UX Design:] Expert in understanding user behavior, semi-structured interviews, surveys, low-fidelity/high-fidelity prototyping (HTML, Flash, Balsamiq, OmniGraffle), interface design guidelines and principles, heuristic evaluation, cognitive walkthrough, online user experiments (A/B testing), lab studies, statistical data analysis using R
  \item[Front-End Development:] Expert in HTML, CSS/Sass, JavaScript, and Flash, familiar with JavaScript frameworks such as jQuery, AngularJS, and D3.js. Famililar with Node.js. Experience with front-end frameworks such as ZURB Foundation, and Twitter Bootstrap.
  \item[Programming Languages:] Expert in Java, familiar with Python, Objective-C, C++, PHP.
  \item[Interpersonal Skills:] Excellent teamwork, communication, and leadership skills
\end{description}
\emph{* please check my website for my portfolio.}

\hrulefill

\section{\sc Education}
{\bf University of British Columbia}, Vancouver, Canada\\
Department of Electrical Engineering and Computer Engineering

\vspace{-.3cm}
{\em PhD, Computer Engineering} \hfill {\bf 2007 - 2014}\\
Supervisor: Dr. Konstantin Beznosov \hfill GPA: 85.2 from 100 \\
Research focus: Human-Computer Interaction, Computer-Supported Cooperative Work, Usable Security and Privacy, Computer Security

{\bf Amirkabir University of Technology}, Tehran, Iran\\
Department of Computer Engineering and Information Technology

\vspace{-.3cm}
{\em M.Sc., Software Engineering} \hfill {\bf 2005 - 2007}\\
{\em B.Sc., Computer Engineering} \hfill {\bf 2001 - 2005}\\

\section{\sc Professional Employment}
{\bf University of British Columbia} {\hfill} {\bf 2007 - 2014}\\
Research Assistant / PhD Student \\
My PhD research topic is a multi-method approach to design usable Identity and Access Management (IAM) systems. As a part of my research, I conducted 19 semi-structured interviews with security professionals, and used grounded theory to analyze and understand usability needs for IAM systems. I also developed a set of domain specific usability heuristics for evaluation of IT security tools, and organized more than 40 heuristic evaluation sessions with usability experts to identify usability problems in one commercial IAM system. Using the results of field and heuristic evaluation studies, I designed a new visualization technique for showing access control policies in organizations. I developed multiple web-based prototypes of the visualization, and conducted a large-scale online user study to evaluate the usability of the prototypes.

{\bf Nokia Siemens Networks (NSN)  Co.} {\hfill} {\bf 2006 - 2007}\\
Solution Engineer, Value-Added Services (VAS) team \\
Designed and developed the Dynamic Prepaid Seamless Expiry (DSED) system using J2EE, JBoss, and Oracle DBMS. The DSED system processed maximum of 36 million charging data record files during a 24-hour window and updated the subscribers' credit expiry data over a 4-hour window. 


{\bf Data Processing (DP) Co.} {\hfill} {\bf 2005 - 2006}\\
Software Engineer, Traffic Control team\\
Served on a team to design and develop a nationwide telecommunication management network. I developed a Java application for management of traffic in telecommunication switches. 

\section{\sc Honors and Awards}
UBC PH.D. Tution Award (2007-2012), and UBC International Partial Tuition Scholarship (2012-2014)

Ranked 3$^{rd}$ in Robocup 2003, The 7th International Competition and Conferences, Padua, Italy, Team S.O.S.
I served on a team of ten undergraduate students and developed intelligent software agents to compete in Robocup rescue simulation competition. 

ACM/ICPC Contest, Ranked 12$^{th}$ out of 94 in Regional Contest 2001, Team AvadaKedavra.

%\section{\sc Research Interests}
%Human Computer Interaction (HCI), Usable Privacy and Security, Computer-Supported Cooperative Work(CSCW), Computer Security, Software Architecture

\section{\sc Selected Publications}
Pooya Jaferian, Hootan Rashtian, and Konstantin Beznosov. 2014. \textbf{To authorize or not authorize: helping users review access policies in organizations}. In Proceedings of the Symposium on Usable Privacy and Security (SOUPS 2014). Pages 301-320. Menlo Park, CA. (acceptance rate: \%26)

Pooya Jaferian, Kirstie Hawkey, Andreas Sotirakopoulos, Maria Velez-Rojas, and Konstantin Beznosov. \textbf{Heuristics for evaluating IT security management tools}. Human-Computer Interaction, Vol. 29, Iss. 4, 2014. (impact factor: 3.039)

Pooya Jaferian, Kirstie Hawkey, Andreas Sotirakopoulos, Maria Velez-Rojas, and Konstantin Beznosov. 2011. \textbf{Heuristics for evaluating IT security management tools}. In Proceedings of the Seventh Symposium on Usable Privacy and Security (SOUPS '11). Pittsburgh, PA, USA, Article 7 , 20 pages. (acceptance rate: \%33, best paper award)

Fahimeh Raja, Kirstie Hawkey, Pooya Jaferian, Konstantin Beznosov, and Kellogg S. Booth. 2010. \textbf{It's Too Complicated, So I Turned It Off! Expectations, Perceptions, and Misconceptions of Personal Firewalls}. In Proceedings of the Third ACM Workshop on Assurable \& Usable Security Configuration (SafeConfig). Pages 53-62. Chicago, IL.

Pooya Jaferian, David Botta, Kirstie Hawkey, and Konstantin Beznosov. 2009. \textbf{A case study of enterprise identity management system adoption in an insurance organization}. In Proceedings of the Symposium on Computer Human Interaction for the Management of Information Technology (CHiMiT '09). Baltimore, MD, Article 7 , 10 pages. (acceptance rate: \%33)

Pooya Jaferian, David Botta, Fahimeh Raja, Kirstie Hawkey, and Konstantin Beznosov. 2008. \textbf{Guidelines for designing IT security management tools}. In Proceedings of the 2nd ACM Symposium on Computer Human Interaction for Management of Information Technology (CHiMiT '08). San Diego, CA, Article 7 , 10 pages. (acceptance rate: \%29)

Rodrigo Werlinger, Kirstie Hawkey, Kasia Muldner, Pooya Jaferian, and Konstantin Beznosov. 2008. \textbf{The challenges of using an intrusion detection system: Is it worth the effort?} In Proceedings of the Symposium on Usable Privacy and Security (SOUPS 2014). Pages 107-116. Pittsburgh, PA. (acceptance rate: \%26)

\section{\sc Teaching Experience}
{\bf Teaching Assistant} {\hfill} {\bf University of British Columbia} \\
Computer and Information System Security (CICS 518){\hfill} {Summer 2014} \\
Human-Computer Interfaces in Engineering Design (EECE 418){\hfill} { Winter 2009, 2011, 2014}  \\
Introduction to Computer Security (EECE 412) {\hfill} {Fall 2013} \\
Software Engineering (EECE 310) {\hfill} { Fall and Winter 2008, 2009, 2010, 2012} \\
Software Engineering Project (EECE 419){\hfill}  {Fall 2011, 2012} \\
Real-Time \& Distributed Systems (CICS 525) {\hfill} {Summer 2009}


\section{\sc Invited Presentations}
P. Jaferian, ``WaterCooler Talk - Improving usability of identity and access management systems'', Invited Talk, CA Technologies, 2012.


P. Jaferian, ``Access and Identity Management'',  Invited Talk, Vancouver Security Special Interest Group, Sierra Systems, Vancouver, Canada, 2010.


P. Jaferian, ``User centered design of ITSM tools'',  Invited Talk, NSERC ISSNet Workshop 2009, Carleton University, Ottawa, Canada, 2009.


P. Jaferian, ``Guidelines for IT security tools'',  Invited Talk, Vancouver Security Special Interest Group, 2009.


P. Jaferian, ``Guidelines for IT security tools'',  Invited Talk, Entrust Inc., Ottawa, Canada, 2008.


\section{\sc Professional Associations}
{\bf Reviewer}\\
Reviewer or external reviewer for: Computer and Security Journal, IEEE Security \& Privacy Magazine, Symposium on Usable Privacy and Security (SOUPS 2014, 2012, 2011), IEEE Security and Privacy Symposium (S\&P 2014), Computer and Communications Security (CCS 2013, 2012), European Symposium on Research in Computer Security (ESORICS 2013), Access Control Models and Technologies (SACMAT 2009), Network \& Distributed System Security (NDSS 2008, 2009, 2011), WEB 2.0 Security and Privacy (W2SP 2009), Symposium on Security and Privacy (S\&P 2009), Annual Computer Security Applications (ACSAC 2008), Computer Human Interaction for the Management of Information Technology (CHIMIT 2008), and New Security Paradigms Workshop (NSPW 2008)

{\bf University Service}\\
Website designer and developer for Laboratory of Education and Research for Secure Systems Engineering (LERSSE), UBCeram, and HCI@UBC \\
Student Volunteer for ISSNET Summer School 2010\\
Student Volunteer for the IEEE/IFIP Conference on Software Architecture (WICSA) 2008\\
Student volunteer for UBC GSS (Graduate Student Society) orientation in 2008\\
Poster designer and photographer for various UBC GSS events\\

\section{\sc Hobbies and Interests}
Yoga, hiking, biking, skiing, running, photography

\end{resume}
\end{document}
